% The main project description file

The story:
\begin{itemize}
    \item Backseat driver: 3 out of 4 Americans are scared of fully autonomous cars [AAA]
    \item In 1900, the driverless elevator was invented - elevators used to have an operator or a 'driver' at all times. It took over fifty years, an elevator operator strike, and a coordinated industry ad campaign for driverless elevators to finally be accepted.
    \item Graceful Handoffs are important - People overtrust..if it works 90\% of time, we think it works 100\% of the time. 
    \item Human in the loop CPS co-design is critical. Generalized to other domains and autonomous systems.
    \item Research has been on modeling human behavior, and interaction.
    \item Specifically want to focus on Trust - hard challenge - trust is a multi-dimensional signal - therefore limit to autonomous vehicles to focus on predictability, and explainability. 
\end{itemize}

\section{Research Description}
%\input{research}



\subsection{Intellectual Merit}

\begin{itemize}
 \item  Scenario based trust modeling:
    \begin{itemize}
        \item Predictability
        \item Explaniability - Local interpretability. 
        \item Situational awareness and feedback
        \item UI interfaces - A/B testing
    \end{itemize} 
  \item Reachability analysis - linked with predictability and safe handoffs.
  \item Human behavior modeling
  \item Behavior guided autonomy
\end{itemize}

\section{Evaluation/Experimentation Plan}
Testbeds/Experiments:
\begin{itemize}
    \item Reachability experiments with ground robots, F1/10 cars.
    \item UI design kit for Autonomous Vehicles (Matlab, Unity, linked with Pre-Scan)
    \item Driving Simulator: Data to measure trust, predictability, explainability, 
    \item Driver attention and behavior.
    \item Virtual reality testbed ?
    \item What metrics will we use?
\end{itemize}


\section{Project Management and Collaboration Plan}
\begin{itemize}
    \item Perrone Robotics - Letter saying they will allow access to their full scale cars and track.
    \item Toyota Research Institute - Support letter saying they are interested in outcomes of this research and will assist in UI development. 
    \item IRB ?
\end{itemize}
\section{Broader Impacts}

